\section{Fingerprint Data}
\label{sec:fingerprint_data}

\subsection{New Imagery}
All \scanners are required to save images in JPEG-2000 format. These images
will be decompressed by \beframework and transmitted as defined in
\Cref{sec:data-interchange}. The participant's \lib shall be able to create
enrollment and search templates from the decompressed versions of the images
created by their \scanner.

Complete guidelines on the required image format are available on
\theprojectwebsite.

\subsection{Background Imagery}
The \lib shall be required to handle creating enrollment and search templates
from a large quantity of ``legacy'' operational rolled imagery. This imagery
will be used to seed an enrollment set on which the \lib will search. Images
may originate from inked fingerprint card scans or live scan devices.

This background imagery shall be provided to the \lib as uncompressed raw 8-bit
grayscale, as transmitted according to \Cref{sec:data-interchange}. The images
will be scanned at $500$ or $1\,000$ pixels per inch horizontal and vertical
resolution. \Libs should call the \code{getResolution()} method on images and
process them into a format suitable for matching, if necessary.

All data provided as background imagery will contain at most one finger.
Fingerprint segmentation routines will not be required.

\subsection{Latent Imagery}
The \lib may support searching latent fingerprint images. These images will
be cropped to include a single latent fingerprint per image. Some exceptions
to this rule may occur due to overlapping prints, but it is expected that
automated latent matching software accounts for such inputs. There are no
guarantees made regarding the orientation of the fingerprint in the image.

Latent images may differ in the number of channels, bits per channel, and
resolution. \Libs should call the \code{getColorDepth()}, \code{getBitDepth()},
and \code{getResolution()} methods on these images and process them into a
format suitable for matching, if necessary.

\subsection{Proprietary Data}
In addition to a JPEG-2000 image, participants have the option to save a
``proprietary'' image or template directly from their \scanner. The time to
create and save this data is included in the recorded physical data acquisition
time for the \scanner, so it may be advisable to extract features using the
API.  This data will be transmitted ``as-is'' to the \lib during enrollment and
search template creation methods.

There are rules and regulations for saving this data to ensure fairness, as
defined on \theprojectwebsite. Not adhering these rules may result in
rejecting the participant's \lib and/or disqualification from the \project. 

